%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\clearpage
\pagetitle{The Cataclysm at Caldor IV}

\begin{columns}

\missionheading{Mission}

The core mission is the same as the Hold and Repel mission in the
Cataclysm packet: Each alliance places three 3 objectives, one each in
their deployment zone, that of the alliance to the left, and neutral
territory.  Each of the primary objectives is a piece of \emph{The
  Scythe} that the teams are trying to secure.  They're worth varying
points to each team because they've already had time to document ones
they hold already, some are ruined in the fighting, others they
believe are more valuable, etc..


Possible: If an alliance achieved a campaign victory in \emph{The
  Debacle} (secured their target) then it can adjust all of the
primary objective markers up to 6''?  Objectives cannot be moved into
or out of deployment zones.

Possible: If alliance won a strategic victory in \emph{The Debacle}
(controlled majority of continents), then its deployment bid is
considered to be 5 minutes less for establishing the order, but not
for how much time they actually have to deploy?

The alliance that won a tactical victory in \emph{The Debacle} got a
slight advantage of going first in choosing missions for the first
round of \emph{The Twilight}.


In turns 4, 5, and 6 there is increasing danger from the world falling
apart: Random chance of earthquakes (all terrain difficult), falling
debris from the space battle overhead (random blast hits), etc..


\missionheading{Campaign Mechanics}

Each player has their legacy card from \emph{The Twilight}.

If they achieved two out of their three Twilight missions in the given
role then they get the legacy bonus given on the card.

If there are multiple declarations to be made at the same time for the
legacy objectives, e.g., ``After all deployment,'' the alliances
alternate in turn order having a player reveal their declaration.

Any secret selections must be unambiguously recorded.

Players must have a model still in the game to claim their Cataclysm
objective.

\missionheading{Scoring}

Campaign results for the alliances are based on control of the primary
objectives (pieces of \emph{The Scythe}).

Individual scores are the sum of victory points from the four Recon
Squad missions (48 total), some points if their alliance wins the
Cataclysm, some points if they achieved their Twilight missions, and a
bunch of points if they achieved their personel Cataclysm objective
(12 points total).

\end{columns}
