%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\clearpage
\pagetitle{Caldor IV}

\begin{columns}
  

  \emph{Caldor IV} is an unofficial, narrative, team-based, campaign
  tournament for Games Workshop's \emph{Warhammer~40,000}.  Set on the
  long beleaguered world of Caldor IV, the campaign chronicles the
  struggle for \emph{The Scythe Of Unbound Light}, an ancient weapon
  of great might.  It is comprised of three parts:

\begin{squishitemize}
\item \textbf{The Debacle:} Three rounds of standard battles to locate
  critical personnel and ancient weaponry before the planet is
  overrun.

\item \textbf{The Twilight:} Four rounds of~200 point Recon Squad
  skirmishes amid the chaos of the all-consuming, inescapable war.

\item \textbf{The Cataclysm:} A single epic battle encompassing all
  the players, throwing~500 point armies into the maelstrom of the
  planet's final hours as they madly fight to secure \emph{The
    Scythe}.
\end{squishitemize}

The Debacle is playable as a straight tournament with some light team
aspects over it.  The Twilight and Cataclysm are more narrative, but
still have a solid tournament basis.  As such, \emph{Caldor IV}
provides the foundation of a great event for both competition and
narrative oriented players.  The campaign is designed to be played
over two full days or several evenings.

The Twilight and The Cataclysm utilize two additional unofficial
\emph{Warhammer~40,000} supplements:

\begin{squishitemize}
\item \textbf{Recon Squad:} Fast playing, simple rules for skirmish
  level play, in which models move and fight
  individually on heavily terrained boards.

\hfill\url{rocketshipgames.com/games/recon-squad/}\hfill\hbox to 0pt{}

\item \textbf{Cataclysm:} Rules, logistics, and mission scenarios for
  large games comprised of multiple players fighting as teams for
  multiple alliances.

\hfill\url{rocketshipgames.com/games/cataclysm/}\hfill\hbox to 0pt{}
\end{squishitemize}

This document outlines mechanics and missions of the campaign.
Additional tips are on the website:

\hfill\url{rocketshipgames.com/games/caldor-iv/}\hfill\hbox to 0pt{}

\missionheading{Campaign Setup and Overview}

To begin, the players are grouped into two or three alliances,
determined by the organizer(s) based on the factions and number of
players participating:

\begin{squishitemize}
\item \textbf{Forces of Order:} The Imperium and its allies;
\item \textbf{Legions of Discord:} Chaos and heretics;
\item \textbf{Spoilers:} Pirates and xenos of all stripes.
\end{squishitemize}

If only two alliances are warranted by the campaign group, they should
play as Order and Discord.

At the outset of the campaign the Legions of Discord have descended on
Caldor IV en masse in search of \emph{The Scythe Of Unbound Light}, a
lost relic of many legends.  Under siege, the Forces of Order are
about to abandon Caldor IV entirely and scorch everything and everyone
left behind.  First, however, the Mechanicum's Magos Ferdinand,
ranking figure on the world, must be retrieved.  Unaware of the true
stakes, the Spoilers have come simply for bloodshed and whatever they
can plunder.

\end{columns}

\vfill
\begin{story}{1.25in}{Treasure In The Darkness}
  Caldor IV---once a luscious knight world, now a smoldering
  husk. Both The Dark Ages and The Heresy it outlasted, but the
  paranoia and isolation of those times set the kernels of future
  failure.  Over the following eons the houses ossified and turned
  inward, gazing at all about them with mistrust, then fear, and
  eventually war.  Centuries of infighting eventually slagged the
  verdant paradise into a charred wasteland.  In recent centuries the
  Mechanicum has resettled the planet, though their motivations for
  doing so are unclear even as their efforts have increased in recent
  decades.  Intrigued, the planet has since been the target of
  continual raids and exploratory incursions by the more intrepid and
  curious pirates, heretics, and xenos.  Weary, stretched to the
  breaking point, the defense forces have finally all but collapsed
  after decades of unceasing combat.  Sensing the weakness, foes of
  the Imperium have all piled in, lusting for blood or other, more
  secret, goals.  Beseeched by the Mechanicum, loyalists throughout
  the sector have poured in to match, deepening the ever swirling
  maelstrom of the planet-wide conflict.  But time and resources have
  run out.
\end{story}
