%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\clearpage
\pagetitle{The Twilight: Mission Pack}


All of the missions are played on a~4'x4' table.

The variable game length rule is used in all missions unless noted otherwise.

A major victory is worth 10 points to the winner and 0 to the loser.
Victory is 7 and 3
Draw is 5 and 5

Plus the two bonus points.

Better victories trump others, e.g., meeting the conditions for a
major victory trumps the conditions for a minor victory.

Missions to be specified in more detail...

\missionheading{Ambush}

The Defender is given an AV10/10/10 HP2 truck with 5 embarked NPCs
with sub-Guardsman stats.  The truck takes dangerous terrain tests on
a 2+ and always takes a dangerous terrain test if it moves flat out.
The truck starts at one end of the board and it or the NPCs must make
it to the far edge.  The Attacker Outflanks.


\missionheading{Assassination}

An NPC with Guardsman-ish stats is placed in control of the Defender,
who loses if it dies.


\missionheading{Battlefield}

Kill points with Dawn of War setup.


\missionheading{Breakthrough}

Attacker has to break into the defender's deployment zone.


\missionheading{Encirclement}

Kill points with the defender starting at the center of the table and
the attacker all around.


\missionheading{Excavation}

Similar to the scouring, several objectives of randomized value are
randomly placed inside a square at table center.  The defender starts
deployed in that square, the attacker is around the edges.


\missionheading{Installation}

A single objective is put forward slightly from the defenders leading
edge, inside an AV11 HP3 Small building.  The defender wins if they
hold that objective.  Otherwise the attacker wins.


\missionheading{Skirmish}

The basic mission from the Recon Squad packet: Vanguard and three objectives.

\newlength{\missionheight}
\setlength{\missionheight}{(\textheight-18pt)/2}
\newcommand{\miwrap}[1]{\noindent\fbox{\vbox to \missionheight{\input{missions/#1}\vfill\vbox to 0pt{}}}}

\newcommand{\mispace}{%
\vfill
%\hrule
%\vspace*{3pt}
%\hrule
%\vfill
}

\newcommand{\mipre}{%
\clearpage
}

\newcommand{\mipost}{%
}

\newcommand{\mipair}[2]{%
\mipre%
\miwrap{#1}%
\mispace%
\miwrap{#2}%
\mipost
}

\newcommand{\scoringbox}[5]{%
\vfill%
\vspace{9pt}%
\noindent\vbox{%
\noindent\vbox to -4pt{\noindent\hfill\Large\bf\sc\fontfamily{ptm}\selectfont Scoring\vbox{}}\\
%
{\fbox{\vbox{\small%
\setlength{\tabcolsep}{2pt}%
\noindent\begin{tabularx}{\linewidth}{cccX}
  \hbox to 1.25em{\rotatebox{45}{\small\bf Attacker}}&
  \hbox to 1.25em{\rotatebox{45}{\small\bf Defender}}&
  &
  \multicolumn{1}{c}{\footnotesize\bf Condition}
\\
  \hline
%
  \rescheck&\rescheck& & {\bf Major Victory:} #1\\
%
  \rescheck&\rescheck& &
  {\bf Minor Victory:} #2\\
%
\rescheck&\rescheck& &
{\bf Draw:} #3\\
\hline \rescheck&\rescheck& &
{\bf Bonus Point:} #4\\
\rescheck&\rescheck& &
{\bf Bonus Point:} #5\\
\end{tabularx}%
}}}}%
}

\clearpage
\squelchbackground

\mipair{ambush}{assassination}
\mipair{battlefield}{breakthrough}
\mipair{encirclement}{excavation}
\mipair{installation}{skirmish}%

\clearpage
\restorebackground
