%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\clearpage
\pagetitle{The Twilight of Caldor IV}

\begin{columns}

  \emph{The Twilight of Caldor IV} is played as four rounds of Recon
  Squad skirmishes between 200 point armies.  Full rules for Recon
  Squad are available here:

\centerline{\url{rocketshipgames.com/games/recon-squad/}}


There are 8 roles:
\begin{squishitemize}
  \item \textbf{Bodyguards:}
  \item \textbf{Demolishers:}
  \item \textbf{Explorators:}
  \item \textbf{Headhunters:}
  \item \textbf{Maulers:}
  \item \textbf{Scouts:}
  \item \textbf{Sentinels:}
  \item \textbf{Warriors:}
\end{squishitemize}

There are 8 missions:
\begin{squishitemize}
\item \textbf{Ambush:}
\item \textbf{Assassination:}
\item \textbf{Battlefield:}
\item \textbf{Breakthrough:}
\item \textbf{Encirclement:}
\item \textbf{Excavation:}
\item \textbf{Installation:}
\item \textbf{Skirmish:}
\end{squishitemize}

\end{columns}

What roles people are playing and whether or not they succeeded at
their campaign missions is public knowledge.

To Cataclysm: If multiple players within an alliance have units
controlling a single objective then they are each considered to hold
it for individual scoring purposes.


If there are multiple declarations to be made at the same time, e.g.,
``After all deployment,'' the alliances alternate in turn order having
a player reveal their declaration.

Any secret selections must be unambiguously recorded.

You must have a model still in the game to claim success.


%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\vfill
\noindent
\begin{minipage}[t]{1.0\linewidth}\centering%
\rowcolors{2}{gray!12}{white}\setlength{\tabcolsep}{3pt}%
\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
\hline
\rowcolor{gray!25} {\bf Mission}       & {\bf Explorators} & {\bf Harriers} & \begin{tabular}[b]{@{}c@{}}\bf Quarter-\\\bf masters\end{tabular} & {\bf Rampagers} & {\bf Sentinels} & {\bf Penetrators} & {\bf Survivors} & {\bf Warriors}\\
%\bf Mission}       & {\bf Explorators} & {\bf Harriers} & {\bf Quartermasters} & {\bf Rampagers} & {\bf Sentinels} & {\bf Penetrators} & {\bf Survivors} & {\bf Warriors}\\
\hline
\hline
{\bf Artifact}      & Either            &                & Either               &                 &                 &                &                 &               \\
{\bf Assassination} &                   & Attacker       &                      &                 &                 &                & Defender        &               \\
{\bf Battlefield}   &                   &                &                      & Either          &                 &                &                 & Either        \\
{\bf Breakthrough}  &                   &                &                      &                 & Defender        & Attacker       &                 &               \\
{\bf Depot}         &                   & Either         & Either               &                 &                 &                &                 &               \\
{\bf Encirclement}  &                   &                &                      & Attacker        &                 &                & Defender        &               \\
{\bf Ground}        & Either            &                &                      &                 &                 &                &                 & Either        \\
{\bf Installation}  &                   &                &                      &                 & Defender        & Attacker       &                 &               \\
\hline
\end{tabular}

\small\it\smallskip
Campaign track mission victory requirement pairs.
\end{minipage}
%%----------------------------------------------------------------------
%%----------------------------------------------------------------------

\clearpage
\squelchbackground

\noindent%
\legacycard{BODYGUARDS}%
{Our lives for you, my liege.\\~}%
{Assassination}%
{Defender}%
{Ambush}%
{Defender}%
{After all deployment, publicly pledge to one of your alliance's
  warlords other than your own.  You succeed if that warlord is in
  play at game end.}%
{Your pledged warlord gains a~5+ Invincible save.  When attached to
  one of your units it always passes Look Out, Sir rolls and your
  attached unit has Counter-Attack and Fearless.}
%%
\hfill
%%
\legacycard{EXCAVATORS}%
{Get it into the crates,\\quickly, this is ours!}  {Excavation}%
{Defender}%
{Skirmish}%
{Either}%
{After all deployment, secretly select a primary objective marker not
  in your deployment zone.  You succeed if you hold that objective at
  game end.}%
{Any model of yours that starts the movement phase in contact with
  \emph{any} marker may move it up to 6'' with the model's movement.
  Markers cannot leave the table or embark.}


\vfill

\noindent%
\legacycard{HEADHUNTERS}%
{Death comes for us all.\\We come for you.}%
{Assassination}%
{Attacker}%
{Ambush}%
{Attacker}%
{After all deployment, secretly select one of the opposing warlords.
  You succeed if that warlord is removed as a casualty by game end.}%
{All of your non-vehicle and walker models are considered to have
  Preferred Enemy, Precision Shot, and Precision Strike when attacking
  the selected warlord or an attached unit.}
%%
\hfill
%%
\legacycard{KILLERS}%
{Kill.  Maim.  Burn.\\~}%
{Battlefield}%
{Either}%
{Encirclement}%
{Attacker}%
{After all deployment, publicly declare a crusade against an opposing
  player.  You succeed at game end if at most 25\% of that player's
  starting army points remain in play.}%
{All of your non-vehicle and walker models have Hatred and Fear when
  attacking that opponent's models.}


\pagebreak

\noindent%
\legacycard{PENETRATORS}%
{Everything has a weak spot.\\~}%
{Installation}%
{Attacker}%
{Breakthrough}%
{Attacker}%
{You succeed if your units control a primary objective marker in an
  opposing deployment zone at game end.}%
{After all deployment you may ruin a piece of terrain or an opposing
  fortification, degrading any associated cover save(s) by~1 to a~6+
  at worst.  All of your non-vehicle and walker models gain Tank
  Hunter.}
%%
\hfill
%%
\legacycard{SCOUTS}%
{Let's go, on the move!\\~}%
{Excavation}%
{Attacker}%
{Skirmish}%
{Either}%
{You succeed if you have controlled at least three different primary
  objective markers outside your deployment zone over the course of
  the game at the end of any of your turns except Turn ~1.}%
% {At the end of each of your turns except the first, make a note for
%   each primary objective marker you control outside your deployment
%   zone which you have not previously controlled.  You succeed if you
%   note at least three.}%
%
{All of your non-vehicle and walker models gain Crusader, Move Through
  Cover, Scout, and Infiltrate.}

\vfill


\noindent%
\legacycard{SENTINELS}%
{None shall pass.\\~}%
{Installation}%
{Defender}%
{Breakthrough}%
{Defender}%
{You succeed if your units control all the primary objective markers
  in your deployment zone at game end.}%
{After all deployment you may bolster a piece of terrain or a
  fortification in your deployment zone, improving any associated
  cover save by~1 to a~2+ at best.  All of your non-vehicle and walker
  models gain Stubborn.}
%%
\hfill
%%
\legacycard{WARRIORS}%
{No rest for the weary.\\~}%
{Battlefield}%
{Either}%
{Encirclement}%
{Defender}%
{You succeed if there are no enemy models even partially in your
  deployment zone at game end.}%
{All of your non-vehicle and walker models gain Feel No Pain (6+) and
  your vehicles gain It Will Not Die.}


\clearpage
\restorebackground


%  Place your choice of
%  an AV 11, HP 3, Small building centered as best as possible on
%  the objective, or 4 segments of barricades.

  The enemy alliance's deployment bid counts as being 5 minutes longer
  for purposes of determining turn order but not deployment time.

  Your alliance's deployment bid counts as being 5 minutes shorter for
  purposes of determining order but not available deployment time.

Your army can field an additional 30 points, which does not count
  toward the percentage calculation above.

  The challenged warlord permanently loses a wound before the start of
  the game, to a minimum of~1.

\missionheading{Cataclysm}

The primary objective markers are pieces of \emph{The Scythe of Unbound Light}.

Some your forces have already been able to document or otherwise
aren't as valuable.  Some have been outright destroyed and are only
minimally useful.  Some are believed to be extremely valuable,
yielding great knowledge even in their fragmented form.
