%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\missiontitle{Mission: Ambush}

\begin{columns}

A supply convoy is moving through the area.

{\bf Attacker:} You must disrupt the shipment.

{\bf Defender:} Your army must get those supplies.


\missionheading{The Battlefield}%

The winner of a~D6 roll off chooses a table edge and the other player
takes the opposite.  Place a small vehicle on the centerline of the
table with its forward edge~6'' from the defender's table edge.  The
defender's deployment zone is the~12'' strip along their table edge.
All of the attacker's units gain Outflank and must be placed in
reserve.

Roll a~D6 before any deployment.  Night Fighting is in effect for
Turn~1 on a~4+; on a~1 or~2 it takes effect on Turn~5 and thereafter.

\missionheading{Mission Rules}%

The attacker plays first.  The defender may not Seize the Initiative.
Half of the attacker's army by the number of models, rounding up,
arrives from reserve on Turn~1.  The remainder arrive as usual.

The vehicle is considered the defender's model in all ways.  It has
armor~11/11/10, ~3 hull points, and may not move Flat Out.  If
immobilized, the vehicle self-repairs and removes that damage result
on a~D6 of~4+ at the start of the defender's movement phase.

\scoringbox%
{Defender if the vehicle is within~6'' of the attacker's table edge.
  Attacker if the vehicle is destroyed and at most~50\% of the
  defender's starting army by points value or models remains.}%
{Defender if the vehicle and more than 50\% of the defender's starting
  army by points value or models remains.  Attacker if at most~50\% of
  the defender's starting army by points value or number of models
  remains.}%
{Otherwise.}%
{Opponent's leader is a casualty.}%
{Player's leader survives.}

\end{columns}
