%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\missiontitle{Mission: Assassination}

\begin{columns}

  A legendary commander has charged to the frontlines of the battle to
  bolster their forces.

  {\bf Attacker:} The commander must be slain.

  {\bf Defender:} They must be defended at all cost.

\missionheading{The Battlefield}%

Deployment zones are 12'' from opposing table edges.  The winner of
a~D6 roll off chooses a side and the other player takes the opposite.
Before deploying, the defender's army gains a commander model.

Place two objective markers, each~24'' from the player table edges
and~12'' from a side edge.

\missionheading{Mission Rules}%

The winner of a~D6 roll off decides to deploy first or second.  After
both players deploy, the player that deployed first chooses to play
first or second.  The player to go second may attempt to Seize the
Initiative.

The commander is an infantry independent character with BS~5 WS~5 S~5
T~5 W~3 I~4 A~2, a~2+ armour save, and a~3+ invulnerable save.  It has
an AP~4 close combat weapon and a ranged weapon with profile Range~12
S~4 AP~5 Assault~2.

\scoringbox%
{Defender if the commander survives and the defender holds more
  objectives.  Attacker if the commander is removed as a casualty and
  the attacker holds more objectives.}%
{Defender if the commander survives, attacker if it is removed as a
  casualty.}%
{\emph{This one's to the death...}}%
{Opponent's leader is a casualty.}%
{Player has a model in opponent's deployment zone.}

\end{columns}
