%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\missiontitle{Mission: Battlefield}

\begin{columns}

  The war grinds on interminably, all notion of battle lines lost in
  the confusion and exhaustion.

  \textbf{Attacker} and \textbf{Defender} roles are identical in this
  mission and have no effect in-game.

\missionheading{The Battlefield}%

The winner of a~D6 roll off chooses a table corner.  Their deployment
zone is the quarter circles of all points within~12'' of that corner
as well as the \emph{diagonally} opposite corner.  The other player's
deployment zone is the~12'' quarter circles from the other corners.

Place a single objective marker at table center.

\missionheading{Mission Rules}%

The winner of a~D6 roll off decides to deploy first or second.  After
both players deploy, the player that deployed first chooses to play
first or second.  The player to go second may attempt to Seize the
Initiative.

Beginning with turn~5, roll a~D6 before the start of the turn.  On
a~4+ Night Fighting is in effect for the remainder of the game.

%\vfill
%\vbox to 0pt{}

\columnbreak
At game end, victory points are earned as follows:

\begin{squishitemize}
\item At least~3 of your opponent's models have been removed as
  casualties: +2

\item At least 50\% of your opponent's army by points value or number
  of models are casualties: +3

\item The total number of wounds lost as a casualty by your opponent
  is more than you: +1

\item All of your opponent's models have been removed as casualties:
  +1
\end{squishitemize}

\vspace*{-2pt}

\scoringbox%
{Player has at least twice as many victory points as their opponent.}%
{Player has more victory points.x}%
{Players have equial victory points.}%
{Opponent's leader is a casualty.}%
{Controls the objective marker.}

\end{columns}
