%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\missiontitle{Mission: Breakthrough}

\begin{columns}

  Opposing forces thrust and counter-thrust to break up or hold
  battlefield positions.

{\bf Attacker:} You must pierce the enemy's lines.

{\bf Defender:} Hold your ground.

\missionheading{The Battlefield}%

The winner of a~D6 roll off chooses a table edge and the other player
takes the opposite.  Deployment zones are~12'' from the players'
respective edges.

\missionheading{Mission Rules}%

The winner of a~D6 roll off decides to deploy first or second.  After
both players deploy, the player that deployed first chooses to play
first or second.  The player to go second may attempt to Seize the
Initiative.

\vfill
\vbox to 0pt{}

\columnbreak

\scoringbox%
{Attacker if at least~50\% of their starting army by points value or
  number of models is at least partially within~6'' of the defender's
  table edge.  Defender if attacker has no models within~6'' of the
  defender's table edge.}%
{Attacker if more than~25\% of their starting army by points value or
  number of models is at least partially within~6'' of the defender's
  table edge.  Defender if attacker has at most 25\% of their starting
  army by points value or number of models within~6'' of the
  defender's table edge.}%
{Otherwise.}%
{Opponent's leader is a casualty.}%
{Player's leader is the closest model to the defender's table edge.}

\end{columns}
