%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\missiontitle{Mission: Excavation}

\begin{columns}

  An important relic was uncovered by an excavation team just before
  they were forced to abandon the site by the encroaching battle.  It
  must be retrieved!

  \textbf{Attacker} and \textbf{Defender} roles are identical in this
  mission and have no effect in-game.

\missionheading{The Battlefield}%

Deployment zones are 12'' from opposing table edges.  The winner of
a~D6 roll off chooses a side and the other player takes the opposite.

Place a primary objective marker at the center of the table and
secondary objective markers at the center of each table quadrant.


\missionheading{Mission Rules}%

The winner of a~D6 roll off decides to deploy first or second.  After
both players deploy, the player that deployed first chooses to play
first or second.  The player to go second may attempt to Seize the
Initiative.

Any model that starts the movement phase in contact with the
\emph{primary} objective marker may move it up to a total of 6'' in
the movement phase with that model.  The marker cannot leave the table
or embark.

%\columnbreak

At game end, control of the primary objective is worth~3 victory
points while each secondary objective is worth~1 victory point.

\scoringbox%
{Player controls the primary objective and has more victory points.}%
{Player has more victory points.}%
{Players have equal victory points.}%
{Opponent's leader is a casualty.}%
{The primary objective marker is fully within your deployment zone.}

\end{columns}
