%%----------------------------------------------------------------------
%%----------------------------------------------------------------------
\missiontitle*{Mission: Skirmish}

\begin{columns}

  Vanguards patrolling the outskirts of their main forces have crashed
  into each other---contact is made!

  \textbf{Attacker} and \textbf{Defender} roles are identical in this
  mission and have no effect in-game.

\missionheading{The Battlefield}%

% A variety of ruins, woods, and other terrain should be placed to
% cover a quarter to a half of the board evenly and roughly
% symmetrically.

Deployment zones are diagonal table corners, up to~12'' from the
centerline between them.  Roll off to determine who chooses a corner
and their player table edge, the other player taking the opposite.

Place objective markers at the center of the table and the centers of
the two table quadrants opposite the deployment zone corners.

\missionheading{Mission Rules}%

The winner of a~D6 roll off decides to deploy first or second.  After
both players deploy, the player that deployed first chooses to play
first or second.  The player to go second may attempt to Seize the
Initiative.

Night Fighting is in effect for Turn~1 on a~D6 of~4+; on a~1 or~2 it
takes effect on Turn~5 and thereafter.

\columnbreak

\scoringbox
{Player controls at least
  two more objective markers than opponent, or opponent has been
  completely eliminated.}
{Player controls at least one more
                       objective marker than opponent.}
{Players control equal objective markers.}
{Opponent's leader is a casualty.}
{Player has at least one model within 12'' of each table corner.}

\end{columns}
